### 2024-04-19 docs/SOSP 2024/results.tex
pass

\begin{figure*}[htb]
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/geomean_speedup_4060_kernel_time_total_time.png}
      \caption{\label{Fig:TBvsRAPIDSTahoe_4060_Speedup}Speedup vs batch size}      
    \end{subfigure}
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/speedup_bar_graph_1024.png}
      \caption{\label{Fig:KernelTimeIndividualBenchmarks4060a} Batch size 1024}
    \end{subfigure}
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/speedup_bar_graph_8192.png}
      \caption{\label{Fig:KernelTimeIndividualBenchmarks4060b} Batch size 8192}
    \end{subfigure}
    % \hfill
    \caption{The first graph shows kernel and total time speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
    benchmarks) across batch sizes on NVIDIA RTX 4060. The bar graphs show kernel time speedup of \Treebeard{} over RAPIDS and Tahoe 
    on NVIDIA RTX 4060. Numbers on the bars are inference times per sample in $\mu$s for RAPIDS and Tahoe.}
\end{figure*}

@@

\begin{figure}[htb]
  \begin{subfigure}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b512_depth8.png}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b4096_depth6.png}
    \caption{}
  \end{subfigure}
  \caption{\label{fig:randomModels4060}Kernel time speedup of \Treebeard{} over RAPIDS for random models
  of max depth 8 at batch size 512 and max depth 6 at batch size 4096.}
\end{figure}

@@

\subsection{Discussion}
Beyond portable performance, our evaluation indicates that \Treebeard{} has several additional advantages over existing systems.
\subsubsection*{Cost Performance trade-off Across Hardware Platforms}
Two of the three GPU targets we use are commodity GPUs that cost less than \$400. They 
are infact much cheaper than the CPU we evaluate on. Despite this, performance on GPUs
is significantly better than on CPUs (by an order of magnitude on RTX 4060).
\Treebeard{} can therefore help data scientists make the best use of 
available processors on their systems.

\subsubsection*{Performance considerations for batch size}
Batch size, exposes a trade-off between latency and throughput. It is not possible to use 
large batch sizes in latency sensitive applications. 
Ideally, one would like 
to maximize performance while respecting the batch size constraint imposed 
by the application. \Treebeard{} enables users to explore this trade-off.

\noindent{}
Overall, our evaluation shows that \Treebeard{} is able to efficiently generate 
high-performance code for processors ranging from NVIDIA and AMD GPUs to Intel CPUs.
On all platforms and models that we tested on, \Treebeard{} significantly outperforms
state-of-the-art systems like RAPIDS, Tahoe and \TreebeardOLD{}.

>>>>

\begin{figure*}[htb]
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/geomean_speedup_4060_kernel_time_total_time.png}
      \caption{\label{Fig:TBvsRAPIDSTahoe_4060_Speedup}Speedup vs batch size}      
    \end{subfigure}
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/speedup_bar_graph_1024.png}
      \caption{\label{Fig:KernelTimeIndividualBenchmarks4060a} Batch size 1024}
    \end{subfigure}
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/speedup_bar_graph_8192.png}
      \caption{\label{Fig:KernelTimeIndividualBenchmarks4060b} Batch size 8192}
    \end{subfigure}
    % \hfill
    \caption{The first graph shows kernel and total time speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
    benchmarks) across batch sizes on NVIDIA RTX 4060. The bar graphs shows the kernel time speedup of \Treebeard{} per benchmark. Numbers on the bars are inference times per sample in $\mu$s for RAPIDS and Tahoe.}
\end{figure*}

@@

\begin{figure}[htb]
  \begin{subfigure}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b512_depth8.png}
    \caption{Batch size 512}
  \end{subfigure}
  \begin{subfigure}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b4096_depth6.png}
    \caption{Batch size 4096}
  \end{subfigure}
  \caption{\label{fig:randomModels4060}Kernel time speedup of \Treebeard{} over RAPIDS for random models.
  }
\end{figure}

@@

\subsection{Additional Observations}
%Beyond portable performance, our evaluation indicates that \Treebeard{} has several additional advantages over existing systems.
\subsubsection*{Cost Performance trade-off Across Hardware Platforms}
Two of the three GPU targets we use are commodity GPUs that cost less than \$400. They 
are infact much cheaper than the CPU we evaluate on. Despite this, performance on GPUs
is significantly better than on CPUs (by an order of magnitude on RTX 4060).
\Treebeard{} can therefore help data scientists make the best use of 
available processors on their systems.

\subsubsection*{A Note on batch size}
Batch size, exposes a trade-off between latency and throughput. It is not possible to use 
large batch sizes in latency sensitive applications. 
Ideally, one would like 
to maximize performance while respecting the batch size constraint imposed 
by the application. \Treebeard{} enables users to explore this trade-off.  
%\subsection*{}
\bigbreak
\noindent
Overall, our evaluation shows that \Treebeard{} is able to efficiently generate 
high-performance code for processors ranging from NVIDIA and AMD GPUs to Intel CPUs.
On all platforms and models that we tested on, \Treebeard{} significantly outperforms
state-of-the-art systems like RAPIDS, Tahoe, XGBoost and \TreebeardOLD{}.
